An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-24 Revision/response.tex

\textcolor{blue}{"For attribute filtering algorithms, factors such as the number of attributes, attribute distribution[12], and attribute  selectivity [46,51] significantly impact algorithm performance."}

%%%%%%%%%%%%%%%%%%%%%% D3 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{In Definition 2.3, $ s_1 $ and $ s_n $ should be replaced with $ a_1 $ and $ a_n $ , respectively.}
	\end{detailed}
}

\noindent
\textbf{Response:} 
Thank you for pointing it out. We sincerely apologize for the misuse of notation in Definition 2.3. This has been corrected in the revised version. (Please see Definition 2.3 in Section 2.1, highlighted in blue in the revised manuscript)

\textcolor{blue}{"Let \( D = \{(v_1, a_1), \ldots, (v_n, a_n)\} \) be a dataset of \( n \) \( d \)-dimensional vectors, each associated with an attribute value \( a_i \)."}

### 2025-07-24 Revision/response.tex

For range filtering, please see section 4.3.1.

\textcolor{blue}{"As for the Search peak memory usage, we can find from the Figure ~\ref{fig:range filtering search peak memory} that it is basically consistent with the Build peak memory usage trend. The algorithm needs to load the complete index into memory during search. Therefore, algorithms with high building overhead, such as WinFilter, also have high search overhead; algorithms with low building overhead, such as Faiss, also have low search overhead. For Milvus, search does not require full index loading and there is additional metadata overhead when building, so the performance is different from the trend."}

%%%%%%%%%%%%%%%%%%%%%% R8 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{metarevision}
		\textit{Run Scalability experiments with larger datasets.}
	\end{metarevision}
}

\noindent
\textbf{Response:} 
Thank you for your valuable suggestion regarding our experiments. In Section 4.2.4 and Section 4.3.4, we have added experiments on the Deep100M dataset. The results show that most algorithms struggle to balance performance with time and space costs on this large-scale dataset. In particular, StitchedVamana performs poorly on Deep100M. For attribute filtering, please see section 4.2.4.

@@

%Thanks to the reviewer for suggesting that there is no explanation in Figure 7 why Vamana is not included. Figure 7 is an experiment on multi-label construction and search, and the Boolean logic of multi-label search is AND. The two algorithms using Vamana, FilteredVamana and StitchedVamana, only support Boolean logic OR for multi-label search, so we did not include them. We will add an explanation of this in the paper.

%All the evaluated algorithms in our experiments build the index in a one-shot manner, without applying any partitioning or merging strategies.
%Additionally, although some of the methods we used—such as FAISS, PUCK, DiskANN, and Milvus—support vector quantization during index construction, we do not enable quantization in any of our experiments. Therefore, the reported index build times do not include quantization.

%%%%%%%%%%%%%%%%%%%%%% D3 %%%%%%%%%%%%%%%%%%%%%%
\myfbox{
	\begin{detailed}
		\textit{The paper lists AF algos (table 1) and RF algos (table 2). It would be good to list the systems in a table with their algos and capabilities (AF, RF, Graph, IVF, ...). Would make it easier to follow the experimental comparison. E.g., Fig 12 does not include Vamana/DiskANN. Should I assume that RF is not possible with Vamana, or just not implemented?}
	\end{detailed}
}

\noindent
\textbf{Response:} 
Thank you for the suggestion. We realized that the original wording is somewhat vague and lead to confusion among readers. To address this, we merged the tables for attribute filtering (AF) and range filtering (RF), and clarified the support of each algorithm for AF and RF in the unified table.

\textcolor{blue}{"The fused table is Table1: Comparison of AF-ANN and RF-ANN search algorithms."}

### 2025-07-24 VLDB2026/main.tex
1

	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}. Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512.

@@

\textit{\textbf{Index construction time.}}
%As shown in Figure~\ref{fig:build_time_comparison_query1}, among the aforementioned 6 datasets, PASE has the longest index construction time due to its single-thread indexing support. Additionally, VBASE also supports only single-thread indexing but achieves better performance than PASE.
\textcolor{orange}{As shown in Figure~\ref{fig:build_time_comparison_query1}, in the above datasets, both PASE and VBASE are single-threaded indexing methods, with PASE having the longest construction time. The on-demand loading and caching strategy used by PASE results in frequent disk I/O and page scheduling, which significantly slow down the construction process. In contrast, VBASE uses full in-memory construction, leading to faster indexing.}

For algorithms supporting 32-thread, ACORN-1 achieves the fastest index construction. This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors. In contrast, ACORN-$\gamma$ incurs the highest index construction time, as it expands neighbor lists and evaluates a large candidate pool, leading to increased computational overhead. \textcolor{orange}{Its construction time on some datasets is even slower than that of the single-threaded VBASE.}

for big dataset:

>>>>

	To investigate the performance of different attribute filtering algorithms during index construction, we evaluate \textcolor{orange}{4} key metrics in the single-attribute scenario: index construction time, index size, \textcolor{orange}{build peak memory and search peak memory}. Notably, PASE on GIST1M and Enron is omitted, as it supports only data with dimensionality less than 512. \textcolor{orange}{Except for algorithms that only support single-threaded construction, all other algorithms are built using 32 threads on the 6 datasets shown in the left figure, and 64 threads on the large-scale Deep100M dataset.}

@@

\textit{\textbf{Index construction time.}}
\textcolor{orange}{Among the six regular-scale datasets shown in the left part of Figure~\ref{fig:build_time_comparison_query1}, the ones with longer build times are mainly PASE, VBASE, and ACORN. PASE and VBASE only support single-threaded builds, and PASE is the slowest to build because its on-demand loading and caching strategies frequently trigger disk I/O and page scheduling, which seriously affects efficiency; VBASE uses full-memory builds and is relatively faster. ACORN-$\gamma$  has a large computational overhead because it needs to expand the neighbor list and evaluate a large number of candidates. The build time on some datasets even exceeds that of single-threaded VBASE. }

\textcolor{orange}{On large-scale dataset Deep100M, besides the three methods already mentioned with long build times, we also find that graph-based algorithms using pruning strategies (such as FilteredDiskANN and UNG) exhibit significantly increased construction time, especially when the pruning is complex and extensive, leading to higher computational overhead. In contrast, the construction time of IVF-based algorithms grows much more slowly with dataset size, thanks to their shard-based design and high parallel efficiency, making them more scalable and advantageous in large-scale scenarios.}

%ACORN-1 achieves the fastest index construction. This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors.

%\textcolor{orange}{As shown in Figure~\ref{fig:build_time_comparison_query1}, in the above datasets, both PASE and VBASE are single-threaded indexing methods, with PASE having the longest construction time. The on-demand loading and caching strategy used by PASE results in frequent disk I/O and page scheduling, which significantly slow down the construction process. In contrast, VBASE uses full in-memory construction, leading to faster indexing.}
%
%
%For algorithms supporting 32-thread, ACORN-1 achieves the fastest index construction. This efficiency stems from its similarity to the original HNSW construction process and the use of a limited number of candidate neighbors. In contrast, ACORN-$\gamma$ incurs the highest index construction time, as it expands neighbor lists and evaluates a large candidate pool, leading to increased computational overhead. \textcolor{orange}{Its construction time on some datasets is even slower than that of the single-threaded VBASE.}
%
%On large dataset Deep100M, VBASE takes longer to build because it only supports single-threaded construction. The other time-consuming algorithms are all graph-based methods, which employ complex pruning strategies during construction to optimize query performance, leading to significantly increased build times.
